The Argennon Virtual Machine

### 2021-04-25 tex/avm.tex
Introduce the Argon language
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

% Preamble
\documentclass[11pt, a4paper]{report}

% Packages
%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\lstset{
%  basicstyle=\ttfamily,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999
\newcommand{\note}[1] {
    \begin{tcolorbox}[colframe=white,colback=white]
        \emph{#1}
        %\emph{#1}\medskip
    \end{tcolorbox}
}

@@

    The Argennon Virtual Machine (AVM) is an abstract computing machine for executing Argennon's smart contracts. The
    Argennon Virtual Machine knows nothing of the Argennon blockchain, only of cleanup sessions and
    execution sessions.

    Execution sessions are separate sessions of executing smart contact's code by the Argennon Virtual Machine.
    These sessions usually are correspondent to the concept of a transaction in a blockchain. (See
    Section~\ref{subsec:execution-sessions})

    A cleanup session is the time slot in which the Argennon Virtual Machine performs cleanup and re-optimization of
    its internal data structures in a "Stop the World" manner. Cleanup sessions usually are done as the final phase of
    the block confirmation process in a blockchain. (See Section ...)

@@

    The Argennon Virtual Machine operates on two kinds of types: primitive types and reference types. There are,
    correspondingly, two kinds of values that can be stored in memory locations, passed as arguments, returned by
    methods, and operated upon: primitive values and reference values.

    Values of primitive or reference types need not be tagged or otherwise be inspectable to determine their types
    at run time, or to be distinguished from values of other types. Instead, the instruction set of the Argennon
    Virtual Machine distinguishes its operand types using instructions intended to operate on values of specific
    types. For instance, \texttt{iadd64} assumes that its operands are two 64-bit signed integers or \texttt{rstore}
    assumes that its operand is a reference type.

    A reference value may be the special \texttt{null} reference, a reference to no location, which will be denoted here
    by \texttt{null}. The default value of a reference type is \texttt{null}.

@@

@@

    All arithmetic operations in the Argennon Virtual machine are safe and there are strict overflow checks and
    blah blah blah

@@

    The Argennon Virtual Machine has five run-time data areas:
    \begin{itemize}
        \item Method Area
        \item Constant Area
        \item Local Frame
        \item Operand Stack
        \item Heap
    \end{itemize}
    All data areas except operand stack, have their own address space. Operand stack is a
    last-in-first-out (LIFO) stack and is not addressable. Every AVM memory access instruction operates on its specific
    data areas.

@@

    Every smart contract has a single constant area which is stored in the AVM code area as a special type of
    non-executable method. The constant area of a smart contract contains several kinds of constants, ranging from user
    defined constants to method address tables. A method address table stores the list of method identifiers of a smart
    contract and their access type. The access type of a method can be either \texttt{external} or \texttt{internal}.
    Only external methods can be invoked by \texttt{invoke\_external} instruction.

@@

    A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
    those chunks that was created by itself. In other words, every memory chunk in the AVM heap has an owner. Only
    the owner can modify a chunk while any one can read that chunk. In addition, for modifying a chunk the \texttt{canModify}
    flag of the current method's \texttt{callInfo} struct must be true.

@@

    The AVM Heap is able to save snapshots of its state and later restore them. This will enable the Argennon
    Virtual Machine to have state reversion capability. The snapshot management of the heap area is done by
    the following functions:
    \begin{itemize}
        \item \texttt{Save()} saves a snapshot of the current state of the heap and pushes it onto the
        snapshot stack.
        \item \texttt{Restore()} pops the snapshot stored on the top of the snapshot stack and restores it. The
        current state of the heap will be lost.
        \item \texttt{Discard()} pops the snapshot stored on the top of the snapshot stack and discards it. The current
        state of the heap will be preserved.
    \end{itemize}

@@

    The Argennon Virtual Machine has four types of method invocation instruction:
    \begin{itemize}
        \item \texttt{invoke\_internal} invokes a method without changing the context of method execution. In other
        words, \texttt{applicationID} and \texttt{canModify} fields of the invoked method in the
        call stack will be the same as the invoker.
        A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
        internal method of another smart contract. Since the invoked method will always be executed in the context of
        the invoking smart contract, a smart contract will not be able to modify another smart contract state by
        this instruction. This instruction facilitates the usage of libraries and code reuse.
        \item \texttt{invoke\_external} invokes a method and changes the context of method execution to another
        smart contract. Only external methods of another smart contract can be called by this instruction. For changing
        the context of method execution this instruction sets the \texttt{applicationID} field of the invoked method
        to the \texttt{applicationID} of the called smart contract. Then it searches the call stack and if
        the \texttt{applicationID} of the called smart contract is found in the call stack it sets \texttt{canModify}
        to \texttt{false}, otherwise \texttt{canModify} is set to \texttt{true}. As a result, if the
        called smart contract is already called, the invoked method will not be able to modify the heap area.
        \item \texttt{invoke\_native} invokes a method that is not hosted by the Argennon Virtual Machine. By this
        instruction, high performance native methods of the hosting machine could become available to AVM smart
        contracts. This instruction will not modify the AVM state.
        \item \texttt{spawn} spawns a new method invocation. Spawning a method invocation is the invocation of a method
        with changing the context of method execution and creating a new call stack. The created call stack is added at
        the end of the call stack queue and the \texttt{canModify} field of the \texttt{CallInfo} struct will always
        be set to \texttt{true}. This instruction does not modify the \texttt{pc} register and the execution of the
        caller will continue after this instruction. As a result, \texttt{spawn} can not return
        any value to the caller and the return value of the called method (if any) will be added
        to the transaction output. If the invoked method completes abruptly it will cause all the call stack queue to
        complete abruptly.
    \end{itemize}

@@

    A method invocation completes normally if that invocation does not cause an exception to be thrown, either
    directly from the AVM or as a result of executing an explicit throw statement. If the invocation of the current
    method completes normally and the invocation was made by an \texttt{invoke} instruction, then a value may be
    returned to the invoking method. This occurs when the invoked method executes one of the return instructions, the
    choice of which must be appropriate for the type of the value being returned (if any). Execution then continues
    normally in the invoking method's local frame with the returned
    value (if any) pushed onto the operand stack. If the method was invoked by a \texttt{spawn} instruction,
    the execution of the next call stack (if any) begins and the returned value
    is appended at the end of the transaction output. When a method invocation completes normally
    the \texttt{Heap.Discard()} function is called as a part of the return instruction.

@@

        \While{\Stack is not empty}
        {
            \Stack.\Pop{}\;
            \eIf{\Stack is not empty \textbf{and} $\Stack[head].pc = catch$}
            {
                \Heap.\Restore{}\;
            }{
                \Heap.\Discard{}\;
            }
        }
        \Heap.\Restore{}\;
        \caption{Abrupt Method Completion}\label{alg:Abrupt}
    \end{algorithm}

    Closer investigation of Algorithm~\ref{alg:Abrupt} shows that when an invocation which was made by
    a \texttt{spawn} instruction completes abruptly, the heap snapshot that was saved before the start of the
    execution of the first call stack of the execution session is restored. This means
    that all changes made to the AVM heap during the execution session will be restored, but the changes made by
    the root smart contract including the transferring of the transaction fee will not be restored.
    See Section~\ref{subsec:execution-sessions} for more details.

    \subsection{Heap Allocation and De-Allocation}\label{subsec:heap-allocation-instructions}

@@

    In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
    from a user to another user, first we need to make sure that the sender has authorized this operation. The
    Argennon virtual machine has no built in mechanism for authorizing operations, but it provides a rich set of
    cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
    passing cryptographic signatures as parameters to methods, a programmer can implement the required logic
    for authorizing any operation.

@@

    \section{Execution Sessions}\label{subsec:execution-sessions}

    The execution of smart contracts code in the AVM is done in execution sessions. Every execution session in the
    Argennon Virtual Machine constitutes of a single method invocation from the \emph{root} smart contract and a list
    of resource allocation requests. These allocation requests always include a request for allocating some amount
    of execution time and a request for accessing some memory locations for reading or writing. If after the start of
    execution an execution session tries to violate its allocated resources, an uncatchable exception will
    be thrown by the AVM\@.

    \note{The AVM does not have a \texttt{calldata} memory area. The arguments of the root smart contract's method will
    be copied from the transaction to the local frame of the invoked method, exactly like a normal method invocation.}

    The root smart contract with the \texttt{applicationID} of zero, is a special smart contract in the Argennon
    Virtual Machine. Its code is immutable and a part of the AVM implementation and always is run in privileged mode.
    Every execution session starts with a call to a method of the root smart contract. This method always transfers
    some amount of fee from an account ot the \texttt{feeSink} account and then it performs the requested operation.

    If the requested operation is a method invocation the root smart contract will call the \texttt{Heap.Save()}
    function once and then it will invoke the requested method using \texttt{spawn} instruction. This means that the
    invoked method will have a separate call stack and if it throws an exception it will not cause a rollback in
    changes the is made by the root smart contract to the state.

    \note{Argennon transactions do not have a sender, and the payer of a transaction fee could be any
    account who has provided the required digital signature.}

    \section{Cleanup Sessions}\label{sec:cleanup-sessions}

@@

>>>>

% Preamble
\documentclass[11pt, a4paper]{report}
\usepackage[a4paper]{geometry}

% Packages
%\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{amsmath}

\lstset{
    language=Java,
    morekeywords={contract, initialize, constructor, external, virtual, map, account, signature, overrides, is, string},
    basicstyle=\small\sffamily,
    columns=fullflexible,
%   keywordstyle=\bfseries,
    breaklines=true,
    showstringspaces=false,
    mathescape
}
%\binoppenalty=99999
%\relpenalty=99999
\newcommand{\note}[1] {
    \begin{tcolorbox}[colframe=white,colback=white]
        \emph{#1}
        %\emph{#1}\medskip
    \end{tcolorbox}
}

@@

    The Argennon Virtual Machine (AVM) is an abstract computing machine for executing Argennon's smart contracts. The
    Argennon Virtual Machine knows nothing of the Argennon blockchain, only of Argennon's identifier tries and
    the concept of execution sessions.

    Execution sessions are separate sessions of executing smart contact's code by the Argennon Virtual Machine.
    These sessions are usually correspondent to the concept of a transaction in a blockchain. (See
    Section~\ref{sec:execution-sessions})

@@

    The Argennon Virtual Machine operates on two kinds of types: primitive types and identifier types. There are,
    correspondingly, two kinds of values that can be stored in memory locations, passed as arguments, returned by
    methods, and operated upon: primitive values and identifier values.

    Values of primitive or identifier types need not be tagged or otherwise be inspectable to determine their types
    at run time, or to be distinguished from values of other types. Instead, the instruction set of the Argennon
    Virtual Machine distinguishes its operand types using instructions intended to operate on values of specific
    types. For instance, \texttt{iadd64} assumes that its operands are two 64-bit signed integers or \texttt{delete}
    assumes that its operand is an identifier type.

    An identifier value in the Argennon Virtual Machine is a variable length array of bytes. Some instructions
    that work with identifiers are able to determine the length of their identifier operands, while some
    other instructions, for performance reasons, require the length to be specified.

@@

    \section{Identifiers}\label{sec:identifiers}

    In the Argennon Virtual Machine four distinct identifier values exist: \texttt{applicationID}, \texttt{accountID},
    \texttt{methodID} and \texttt{chunkID}.

    All these identifiers are \emph{prefix codes}, and hence can be represented by
    \emph{prefix trees} \footnote{Also knows as tries.}. The AVM has three primitive prefix trees:
    \emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
    prefix code built by using one or more of these prefix trees:
    \begin{itemize}
        \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
        \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree.
        \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
        a prefix code made by \emph{local} prefix tree.(\texttt{|} is the concatenating operator.)

        \texttt{methodID = (applicationID|<local prefix code>)}
        \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
        an \texttt{accountID} to a prefix code made by \emph{local} prefix tree

        \texttt{chunkID = (applicationID|accountID|<local prefix code>)}
    \end{itemize}

    All Argennon prefix trees have an equal branching factor \(\beta\). Therefore, we can represent an Argennon
    prefix tree as a sequence of fractional numbers in base \(\beta\):
    \[
        <A^{(1)},A^{(2)},A^{(3)},\dots>
    \]
    Where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)}<A^{(i+1)}\). A typical choice for \(\beta\)
    could be \(2^8\).

    One important property of prefix identifiers is that while they have variable and unlimited length, they are
    uniquely extractable from any data. Assume that we have a string of digits which are in base $\beta$, we
    know that $k$ first digits belong to an Argennon's identifier, but we don't know the value of $k$.
    Algorithm~\ref{alg:prefix_id} can extract the prefixed identifier uniquely. We can apply this algorithm
    multiple times to a sequence to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

    %##\includegraphics[width=17cm]{../img/Alg1s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
        {Txns}{$T$}
        \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
        \Input{A sequence of $n$ digits in base $\beta$: $d_{1}d_{2}\dots d_{n}$ \newline
            A prefix tree: $<A^{(1)},A^{(2)},A^{(3)},\dots>$}
        \Output{Valid identifier prefix of the sequence.}
        \BlankLine
        \For{$i = 1$ \KwTo $n$}
        {
            \If{$(0.d_{1}d_{2}\dots d_{i})_\beta < A^{(i)}$}
            {
                \KwRet{$d_{1}d_{2}\dots d_{i}$}\;
            }
        }
        \KwRet{NIL}\;
        \caption{Finding a prefixed identifier}\label{alg:prefix_id}
    \end{algorithm}

    In Argennon the shorter prefix codes are assigned to more active accounts and smart contracts which tend to own more
    data objects in the system. The prefix trees are designed by analyzing empirical data to make sure the number
    of leaves in each level is chosen appropriately.

@@

    The Argennon Virtual Machine supports signed integer and signed floating point operations. The Argennon Virtual
    Machine does not support any type of unsigned arithmetics. All arithmetic operations in the Argennon Virtual Machine
    are checked and any type of overflow or underflow will cause a catchable exception to be thrown.

@@

    The Argennon Virtual Machine has five run-time data areas:
    \begin{itemize}
        \item Method Area
        \item Constant Area
        \item Local Frame
        \item Operand Stack
        \item Heap
    \end{itemize}
    All data areas except operand stack, have their own address space. Operand stack is a
    last-in-first-out (LIFO) stack and is not addressable. Every AVM instruction operates on its specific
    data areas.

@@

    Every smart contract has a single constant area which is stored in the AVM code area as a special type of
    non-executable method. The constant area of a smart contract contains several kinds of constants, ranging from user
    defined constants to method address tables. A method address table stores the list of methods of a smart
    contract and their access type. The access type of method can be either \texttt{external} or \texttt{internal}.
    Only external methods can be invoked by \texttt{invoke\_external} instruction.

@@

    A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
    those chunks that was created by itself. In other words, every memory chunk in the AVM heap has an owner. Only
    the owner can modify a chunk while anyone can read that chunk. In addition, for modifying a chunk the \texttt{canModify}
    flag of the current method's \texttt{callInfo} struct must be true. The owner of a chunk can be easily determined
    by the \texttt{applicationID} part of the chunk identifier.

@@

    The AVM Heap is able to save snapshots of its state and later restore them. This will enable the Argennon
    Virtual Machine to have state reversion capability. The snapshot management of the heap area is done by
    the following functions:
    \begin{itemize}
        \item \texttt{Save()} saves a snapshot of the current state of the heap and pushes it onto the
        snapshot stack.
        \item \texttt{Restore()} pops the snapshot stored on the top of the snapshot stack and restores it. The
        current state of the heap will be lost.
        \item \texttt{Discard()} pops the snapshot stored on the top of the snapshot stack and discards it. The current
        state of the heap will not change.
    \end{itemize}

@@

    The Argennon Virtual Machine has four types of method invocation instruction:
    \begin{itemize}
        \item \texttt{invoke\_internal}: invokes a method without changing the context of method execution. In other
        words, \texttt{applicationID} and \texttt{canModify} fields of the invoked method in the
        call stack will be the same as the invoker.
        A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
        internal method of another smart contract. Since the invoked method will always be executed in the context of
        the invoking smart contract, a smart contract will not be able to modify another smart contract state by
        this instruction. This instruction facilitates code reuse and the usage of libraries.
        \item \texttt{invoke\_external}: invokes a method and changes the context of method execution to another
        smart contract. Only external methods of another smart contract can be called by this instruction. For changing
        the context of method execution this instruction sets the \texttt{applicationID} field of the invoked method
        to the \texttt{applicationID} of the called smart contract. Then it searches the call stack and if
        the \texttt{applicationID} of the called smart contract is found in the current call stack it sets
        \texttt{canModify} to \texttt{false}, otherwise \texttt{canModify} is set to \texttt{true}.
        As a result, if the called smart contract is already called, the invoked method will not be
        able to modify the heap area.
        \item \texttt{invoke\_native}: invokes a method that is not hosted by the Argennon Virtual Machine. By this
        instruction, high performance native methods of the hosting machine could become available to AVM smart
        contracts. This instruction will not modify the AVM state.
        \item \texttt{spawn}: spawns a new method invocation. Spawning a method invocation is the invocation of a method
        with changing the context of method execution and creating a new call stack. Only external methods can
        be spawned. The created call stack is added at the end of the call stack queue and
        the \texttt{canModify} field of the pushed \texttt{CallInfo} struct will always
        be set to \texttt{true}. This instruction does not modify the \texttt{pc} register and the execution of the
        caller will continue after this instruction. As a result, \texttt{spawn} can not return
        any value to the caller and the return value of the called method (if any) will be added
        to the transaction output. If the invoked method completes abruptly, it will cause all the call stack queue to
        complete abruptly.
    \end{itemize}

@@

    A method invocation completes normally if that invocation does not cause an exception to be thrown, either
    directly from the AVM or as a result of executing an explicit throw statement. If the invocation of the current
    method completes normally and the invocation was made by an \texttt{invoke} instruction, then a value may be
    returned to the invoking method. This occurs when the invoked method executes one of the return instructions, the
    choice of which must be appropriate for the type of the value being returned (if any). Execution then continues
    normally in the invoking method's local frame with the returned
    value (if any) pushed onto the operand stack. If the method was invoked by a \texttt{spawn} instruction,
    the execution of the next call stack (if any) begins and the returned value
    is appended at the end of the transaction output. When a method invocation completes normally,
    the \texttt{Heap.Discard()} function is called as a part of the return instruction.

@@

        \While{\Stack is not empty}
        {
            \Stack.\Pop{}\;
            \eIf{\Stack is not empty \textbf{and} $\Stack[head].pc \rightarrow catch$}
            {
                \Heap.\Restore{}\;
            }{
                \Heap.\Discard{}\;
            }
        }
        \Heap.\Restore{}\;
        \caption{Abrupt method completion}\label{alg:Abrupt}
    \end{algorithm}

    A closer investigation of Algorithm~\ref{alg:Abrupt} shows that when an invocation which was made by
    a \texttt{spawn} instruction completes abruptly, the heap snapshot that was saved before the start of the
    execution of the first call stack of the execution session is restored. Since the root
    smart contract calls \texttt{Heap.Save()} function before spawning the requested method, this means
    that all changes made to the AVM heap during the execution session will be restored, but the changes made by
    the root smart contract including the transferring of the transaction fee will not be restored. See
    Section~\ref{sec:execution-sessions} for more details.

    \subsection{Heap Allocation and Deallocation}\label{subsec:heap-allocation-instructions}

    Heap allocation and deallocation in the Argennon Virtual Machine is done by the following instructions:

    \begin{itemize}
        \item \texttt{alloc}: creates a new memory chunk of the specifies size in the heap. the identifier
        of the new chunk will be the concatenation of the \texttt{applicationID} of the creator of the chunk and
        the \texttt{id} operand. The specified identifier must be concatenation of
        an \texttt{accountID} and a prefix code
        generated by the \emph{local} prefix tree: \texttt{id = accountID|localID}. If the identifier is not valid or
        if it already exists in the heap a catchable exception will be thrown.

        \item \texttt{delete}: deletes the chunk that its identifier is the concatenation of the current smart
        contract \texttt{applicationID} to the specified \texttt{id}. If the identifier is not valid or
        if the chunk was not found a catchable exception will be thrown.
    \end{itemize}

    When a smart contract allocates a new memory chunk, the identifier of the new chunk is not generated by
    the AVM, instead the smart contract can choose an identifier itself. This is a very important feature of
    the AVM heap which allows smart contracts to use the AVM heap as a dictionary (map) data structure.
    Because the \texttt{chunkID} is a prefix code, any smart contract has its own identifier space and a smart contract
    can easily generate unique identifiers for its chunks.

    The AVM requires the chosen identifier to be a prefix code made by concatenating a code compatible with
    the \emph{accounts} prefix tree to a code compatible with the \emph{local} prefix tree. This requirement will
    enable AVM to detect invalid identifiers while smart contracts can easily associate data with account identifiers.
    At the same time, A smart contract is able to create maps with costume keys by appending local identifiers
    to the \texttt{accountID} zero, which does not correspond to a valid account in the Argennon.

    \section{Execution Sessions}\label{sec:execution-sessions}

    The execution of smart contracts code in the AVM is done in execution sessions. Every execution session in the
    Argennon Virtual Machine consists of a single method invocation from the \emph{root} smart contract and a list
    of resource allocation requests. These allocation requests always include a request for allocating some amount
    of execution time and a request for accessing some memory locations for reading or writing. If after the start
    an execution session tries to violate its allocated resources, an \textbf{uncatchable} exception will
    be thrown by the AVM\@.

    \note{The AVM does not have a \texttt{calldata} memory area. The arguments of the root smart contract method will
    be copied from the transaction to the local frame of the invoked method, exactly like a normal method invocation.}

    The root smart contract with the \texttt{applicationID} of zero, is a special smart contract in the Argennon
    Virtual Machine. Its code is immutable and is a part of the AVM implementation. The root smart contract is always
    run in the privileged mode, and every execution session starts with a call to a method of the root smart contract.
    This method always transfers some amount of fee from an account ot the \texttt{feeSink} account and then it
    performs the requested operation.

    \note{Argennon transactions do not have a sender, and the payer of the transaction fee could be any
    account who has provided the required digital signature.}

    If the requested operation is a method invocation, the root smart contract will call the \texttt{Heap.Save()}
    function once, and then it will invoke the requested method using \texttt{spawn} instruction. This means that the
    invoked method will have a separate call stack and if it completes abruptly the changes made by the root
    smart contract to the state will not be reverted.

@@

    In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
    from a user to another user, first we need to make sure that the sender has authorized this operation. The
    Argennon virtual machine has no built-in mechanism for authorizing operations, but it provides a rich set of
    cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
    passing cryptographic signatures as parameters to methods, a programmer can implement the required logic
    for authorizing any operation.

@@

@@

    \chapter{The Argon Language}\label{ch:argon-lang}

    \section{Introduction}\label{sec:introduction2}

    The Argon programming language is a class-based, object-oriented language designed for writing Argennon's smart
    contracts. The Argon programming language is inspired by Solidity and is similar to Java, with a number of aspects
    of them omitted and a few ideas from other languages included. Argon is designed to be fully compatible with
    the Argennon Virtual Machine and be able to use all advanced features of the Argennon blockchain.

    Argon Programs are organized as sets of packages. Each package has its own set of names for types, which helps
    to prevent name conflicts. Every package can contain an arbitrary number of classes and a single contract. Every
    Argon package corresponds to at max one AVM smart contract.

    \section{Features Overview}\label{sec:features-overview}

    \subsection{Static Classes}\label{subsec:static-classes}

    In Argon a static class is an uninstantiable class which all its members and methods are static. Every static
    class can define a special method \texttt{initialize} which can only be called in the \texttt{initialize}
    method of the single contract of the package the static class is defined in.

    A Static class is like a normal class which can only have one instance. So like normal classes, static classes can
    be a super class or a subclass of other static classes and can implement interfaces.

    \subsection{Contracts}\label{subsec:contract}

    Every package of an Argon program can have one or zero contracts. A contact is a special static class which is
    allowed to define methods with \texttt{external} visibility. When an Argon package is deployed as an AVM smart
    contract, these external methods will define the contract's public interface.

    \subsection{Access Level Modifiers}\label{subsec:access-level-modifiers}

    Access level modifiers determine whether other classes can use a particular field or invoke a particular method or
    if a method can be invoked externally by other smart contracts.

    \begin{center}
        \begin{tabular}{lllllr}
            \hline
                    & Class & Package & Subclass & Program & World \\
            \hline
            private   & yes   & no      & no       & no      & no    \\
            protected & yes   & no      & yes      & no      & no    \\
            package   & yes   & yes     & yes      & no      & no    \\
            public    & yes   & yes     & yes      & yes     & no    \\
            external  & no    & no      & no       & no      & yes   \\
            \hline
        \end{tabular}\label{tab:table}
    \end{center}

    \begin{lstlisting}[frame=TB, float, title=Argon contracts are static classes,label={lst:code1}]
// A contract is a static class and all its methods are automatically static.
contract MirrorToken {
    private SimpleToken token;
    private SimpleToken reflection;

    // `initialize` is a special static method that is called by the AVM after the code of a contract
    // is stored in the AVM code area. It can not be called after that.
    initialize(double supply1, double supply2) {
    // `new` does not create a new smart contract. It just makes an ordinary object.
        token = new SimpleToken(supply1);
        reflection = new SimpleToken(supply2);
    }

    external void transfer(account sender, account recipient,
        double amount, signature sig) {
        // Checks if the signature is issued by the sender and verifies the calling of this function
        // with the current parameters.
        sig.verifyCallBy(sender);
        token.transfer(sender, recipient, amount);
        reflection.transfer(recipient, sender, Math.sqrt(amount));
    }

    external double balanceOf(account user) { return token.balanceOf(user); }

    external double balanceOfReflection(account user) { return reflection.balanceOf(user); }
}

public static class Math {
    public double sqrt(double x) {
        return // calculate square root of x
    }
}

package class SimpleToken {
    private map(account -> double) balances;

    // The visibility of a member without an access modifier will be the same as its defining
    // class so `SimpleToken` constructor has package visibility.
    constructor(double initialSupply) {
        // initializes the object
    }

    void transfer(account sender, account recipient, double amount) {
        if (balances[sender] < amount) throw("Not enough balance.");
        // implements the required logic...
    }
    // implements other methods...
}
    \end{lstlisting}

    \subsection{Shadowing}\label{subsec:shadowing}

    If a declaration of a type (such as a member variable or a parameter name) in a particular scope (such as an
    inner block or a method definition) has the same name as another declaration in the enclosing scope, it will
    result in a compiler error. In other words, the Argon programming language does not allow shadowing.
